---
title: "Pruebas"
author: "Oscar Centeno Mora - IAM"
date: "6 de marzo de 2019"
output: html_document
---

---
title: "Visualización univariada, multivariada y el Story-line"
author: "Oscar Centeno Mora"
date: " "
output: 
   html_document: 
       toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(plotly)
library(DT)
library(ggplot2)
library(forecast)
library(tidyverse)
library(date)
library(lubridate)
library(xts)        # To make the convertion data-frame / xts format
library(dygraphs)
library(ggExtra)
library(plotly)
library(gapminder)
library(gridExtra)
library(rattle)
library(ggridges)
library(vioplot)
library(likert)
library(fmsb) 
library(wordcloud)
library(reshape)
library(tm)
library(GGally)
library(car)
library(RColorBrewer)
library(ellipse)
library(corrgram)
library(treemap)
library(d3Tree)
library(dendextend)
library(ggraph)
library(igraph)
library(networkD3)
library(circlize)
library(ggmap)
library(cartography)

library(maps)
library(geosphere)


```

<style>
table {
background-color:#FFFFFF;
}
</style>

<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: darkblue;
}
</style>

<button onclick="document.body.scrollTop = document.documentElement.scrollTop = 0;" style="
    position: fixed;
    bottom: 5px;
    right: 40px;
    text-align: center;
    cursor: pointer;
    outline: none;
    color: #fff;
    background-color: #0A71A0;
    border: none;
    border-radius: 15px;
    
">Ir arriba</button>


# Formas de visualizar la información {.tabset .tabset-fade .tabset-pills}

## Visualización multivariada  {.tabset .tabset-fade}

### Mapas


```{r echo=FALSE, error=FALSE ,message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
map('world',col="#f2f2f2", fill=TRUE, bg="white", lwd=0.05,mar=rep(0,4),border=0, ylim=c(-80,80) )



Buenos_aires=c(-58,-34)
Paris=c(2,49)
Melbourne=c(145,-38)
data=rbind(Buenos_aires, Paris, Melbourne) %>% as.data.frame()
colnames(data)=c("long","lat")



points(x=data$long, y=data$lat, col="slateblue", cex=3, pch=20)

# Connection between Buenos Aires and Paris
inter <- gcIntermediate(Paris,  Buenos_aires, n=50, addStartEnd=TRUE, breakAtDateLine=F)             
lines(inter, col="slateblue", lwd=2)
 
# Between Paris and Melbourne
inter <- gcIntermediate(Melbourne,  Paris, n=50, addStartEnd=TRUE, breakAtDateLine=F)             
lines(inter, col="slateblue", lwd=2)


```


```{r echo=FALSE, error=FALSE ,message=FALSE, warning=FALSE}

plot_my_connection=function( dep_lon, dep_lat, arr_lon, arr_lat, ...){
	inter <- gcIntermediate(c(dep_lon, dep_lat), c(arr_lon, arr_lat), n=50, addStartEnd=TRUE, breakAtDateLine=F)             
	inter=data.frame(inter)
	diff_of_lon=abs(dep_lon) + abs(arr_lon)
	if(diff_of_lon > 180){
		lines(subset(inter, lon>=0), ...)
		lines(subset(inter, lon<0), ...)
	}else{
		lines(inter, ...)
		}
}

map('world',col="#f2f2f2", fill=TRUE, bg="white", lwd=0.05,mar=rep(0,4),border=0, ylim=c(-80,80) )
points(x=data$long, y=data$lat, col="slateblue", cex=3, pch=20)
 
plot_my_connection(Paris[1], Paris[2], Melbourne[1], Melbourne[2], col="slateblue", lwd=2)
plot_my_connection(Buenos_aires[1], Buenos_aires[2], Melbourne[1], Melbourne[2], col="slateblue", lwd=2)
plot_my_connection(Buenos_aires[1], Buenos_aires[2], Paris[1], Paris[2], col="slateblue", lwd=2)


```


```{r echo=FALSE, error=FALSE ,message=FALSE, warning=FALSE}

data=rbind(
	Buenos_aires=c(-58,-34),
	Paris=c(2,49),
	Melbourne=c(145,-38),
	Saint.Petersburg=c(30.32, 59.93),
	Abidjan=c(-4.03, 5.33),
	Montreal=c(-73.57, 45.52),
	Nairobi=c(36.82, -1.29),
	Salvador=c(-38.5, -12.97)
	)  %>% as.data.frame()
colnames(data)=c("long","lat")

all_pairs=cbind(t(combn(data$long, 2)), t(combn(data$lat, 2))) %>% as.data.frame()
colnames(all_pairs)=c("long1","long2","lat1","lat2")

# background map
par(mar=c(0,0,0,0))
map('world',col="#f2f2f2", fill=TRUE, bg="white", lwd=0.05,mar=rep(0,4),border=0, ylim=c(-80,80) )
 
# add every connections:
for(i in 1:nrow(all_pairs)){
	plot_my_connection(all_pairs$long1[i], all_pairs$lat1[i], all_pairs$long2[i], all_pairs$lat2[i], col="skyblue", lwd=1)
	}
 
# add points and names of cities
points(x=data$long, y=data$lat, col="slateblue", cex=2, pch=20)
text(rownames(data), x=data$long, y=data$lat,  col="slateblue", cex=1, pos=4)

```

```{r echo=FALSE, error=FALSE ,message=FALSE, warning=FALSE}

# A function that keeps the good part of the great circle, by Jeff Leek:
getGreatCircle = function(userLL,relationLL){
  tmpCircle = greatCircle(userLL,relationLL, n=200)
  start = which.min(abs(tmpCircle[,1] - data.frame(userLL)[1,1]))
  end = which.min(abs(tmpCircle[,1] - relationLL[1]))
  greatC = tmpCircle[start:end,]
  return(greatC)
}

# map 3 connections:
map('world',col="#f2f2f2", fill=TRUE, bg="white", lwd=0.05,mar=rep(0,4),border=0, ylim=c(-80,80) )
great=getGreatCircle(Paris, Melbourne)
lines(great, col="skyblue", lwd=2)
great=getGreatCircle(Buenos_aires, Melbourne)
lines(great, col="skyblue", lwd=2)
great=getGreatCircle(Paris, Buenos_aires)
lines(great, col="skyblue", lwd=2)
points(x=data$long, y=data$lat, col="slateblue", cex=3, pch=20)
text(rownames(data), x=data$long, y=data$lat,  col="slateblue", cex=1, pos=4)
```



